---
title: "MAGeCK-VISPR Quality Check"
author: "Dian Li, Wubing Zhang, Zexian Davis Zeng"
site: workflowr::wflow_site
date: "`r Sys.Date()`"
output: 
  workflowr::wflow_html:
    toc: false
    number_sections: true
    toc_depth: 1
    df_print: paged
    css: style.css
    toc_float:
      collapsed: false
      smooth_scroll: true
editor_options:
  chunk_output_type: console
description: "This document contains quality check (QC) results for running MAGeCK-VISPR 'test' module on CRISPR data."
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(cache = FALSE, message = FALSE)
library(workflowr)
library(DT)
```

# **Introduction**

<br />
This document contains quality check (QC) results from running **MAGeCK-VISPR** _test_ module on immune-related CRISPR data. We have annotated the results into four major categories: <br />
<br />
1. <a href="01-essentiality.html">**Essentiality screen**</a><br />
2. <a href="02-sorting.html">**Sorting screen**</a><br />
3. <a href="03-coculture.html">**Coculture screen**</a><br />
4. <a href="04-invivo.html">**In-vivo screen**</a><br />


---

# **Coculture screen**

## **Coculture-NK**

<br />
```{r, echo=FALSE, cache = FALSE}
df = read.csv("../docs/data_list.csv", sep = ",", header=TRUE)
df = df[grep("Coculture-NK", df$Category, ignore.case = T), -grep("SubDir|Category", colnames(df), ignore.case = T)]
rownames(df) = 1:dim(df)[1]
# datatable(df,  rownames=TRUE, escape=FALSE, filter = 'top', options = list(pageLength = 25, autoWidth = TRUE))
datatable(df,  rownames=TRUE, escape=FALSE, options = list(pageLength = 50, autoWidth = TRUE), callback = JS("
    table.on( 'order.dt search.dt', function () {
        table.column(0, {search:'applied', order:'applied'}).nodes().each( 
            function (cell, i) {
                cell.innerHTML = i+1;
            } );
    } )")) %>% formatStyle(0, target= 'row', lineHeight='100%')
```

---

## **Coculture-T**

<br />
```{r, echo=FALSE, cache = FALSE}
df = read.csv("../docs/data_list.csv", sep = ",", header=TRUE)
df = df[grep("Coculture-T", df$Category, ignore.case = T), -grep("SubDir|Category", colnames(df), ignore.case = T)]
rownames(df) = 1:dim(df)[1]
# datatable(df,  rownames=TRUE, escape=FALSE, filter = 'top', options = list(pageLength = 25, autoWidth = TRUE))
datatable(df,  rownames=TRUE, escape=FALSE, options = list(pageLength = 50, autoWidth = TRUE), callback = JS("
    table.on( 'order.dt search.dt', function () {
        table.column(0, {search:'applied', order:'applied'}).nodes().each( 
            function (cell, i) {
                cell.innerHTML = i+1;
            } );
    } )")) %>% formatStyle(0, target= 'row', lineHeight='100%')
```

---

# **Essentiality screen**

<br />
```{r, echo=FALSE, cache = FALSE}
df = read.csv("../docs/data_list.csv", sep = ",", header=TRUE)
df = df[grep("Essentiality|SyntheticLethal", df$Category, ignore.case = T), -grep("SubDir|Category", colnames(df), ignore.case = T)]
rownames(df) = 1:dim(df)[1]
# datatable(df,  rownames=TRUE, escape=FALSE, filter = 'top', options = list(pageLength = 25, autoWidth = TRUE))
datatable(df,  rownames=TRUE, escape=FALSE, options = list(pageLength = 50, autoWidth = TRUE), callback = JS("
    table.on( 'order.dt search.dt', function () {
        table.column(0, {search:'applied', order:'applied'}).nodes().each( 
            function (cell, i) {
                cell.innerHTML = i+1;
            } );
    } )")) %>% formatStyle(0, target= 'row', lineHeight='100%')
```

---

# **In-vivo screen**

<br />
```{r, echo=FALSE, cache = FALSE}
df = read.csv("../docs/data_list.csv", sep = ",", header=TRUE)
df = df[grep("Invivo|In-vivo", df$Category, ignore.case = T), -grep("SubDir|Category", colnames(df), ignore.case = T)]
rownames(df) = 1:dim(df)[1]
# datatable(df,  rownames=TRUE, escape=FALSE, filter = 'top', options = list(pageLength = 25, autoWidth = TRUE))
datatable(df,  rownames=TRUE, escape=FALSE, options = list(pageLength = 50, autoWidth = TRUE), callback = JS("
    table.on( 'order.dt search.dt', function () {
        table.column(0, {search:'applied', order:'applied'}).nodes().each( 
            function (cell, i) {
                cell.innerHTML = i+1;
            } );
    } )")) %>% formatStyle(0, target= 'row', lineHeight='100%')
```

---

# **Sorting screen**

<br />
```{r, echo=FALSE, cache = FALSE}
df = read.csv("../docs/data_list.csv", sep = ",", header=TRUE)
df = df[grep("Sorting", df$Category, ignore.case = T), -grep("SubDir|Category", colnames(df), ignore.case = T)]
rownames(df) = 1:dim(df)[1]
# datatable(df,  rownames=TRUE, escape=FALSE, filter = 'top', options = list(pageLength = 25, autoWidth = TRUE))
datatable(df,  rownames=TRUE, escape=FALSE, options = list(pageLength = 50, autoWidth = TRUE), callback = JS("
    table.on( 'order.dt search.dt', function () {
        table.column(0, {search:'applied', order:'applied'}).nodes().each( 
            function (cell, i) {
                cell.innerHTML = i+1;
            } );
    } )")) %>% formatStyle(0, target= 'row', lineHeight='100%')
```

---

# **Additional links**

<br />
1. <a href="https://bitbucket.org/liulab/mageck-vispr/src/master/">MAGeCK-VISPR Installation</a><br />
2. <a href="https://builderpie.github.io/run_MAGeCK-VISPR/32968282_JasonMoffat_Nature_2020.html">32968282_JasonMoffat_Nature_2020</a><br />

---
